A Survey on Ordered Binary Decision Diagrams

### 2015-09-11 paper.tex
Finish Compose operation
Restructure
Finish Satisfy operation

\noindent
The time complexity then improves to be
$O\left(|V_{f_1}|^2 \cdot |V_{f_2}|\right)$~\cite{BRYANT86}. \tbr

@@

>>>>

\noindent
The time complexity then improves to be
$O\left(|V_{f_1}|^2 \cdot |V_{f_2}|\right)$~\cite{BRYANT86}.
~\cite[p. 686]{BRYANT86} lists Bryant's full pseudocode.

Bryant~\cite{BRYANT86} also described another, even more efficient way to compose
two function graphs. But this approach only applicable under restricted conditions.
\tbr

@@

In essence, Bryant~\cite{BRYANT86} described two operations, i.e.
\textit{Satisfy-one} and \textit{Satisfy-all}, both operating on the satisfying
set. As the name suggests, \textit{Satisfy-one} selects a single element and
\textit{Satisfy-all} selects all elements from the satisfying set.

\textit{Satisfy-one} traverses the OBDD depth-first and uses backtracking until
a terminal node of the constant function \textbf{1} is encountered. If such a
node is found, the corresponding Boolean function is satisfiable and true is
returned. Furthermore, an array representing the satisfying variable assignment
is assigned. The time complexity for a reduced graph is linear, i.e.
$O(|V_f|)$~\cite{BRYANT86}.

\textit{Satisfy-all} also traverses the OBDD depth-first. Every time the terminal
node having value \textbf{1} is traversed, it is printed. The recursive procedure
terminates as soon as the terminal node having value \textbf{0} is reached. This
results in a time complexity of $O(|V_f| \cdot |S_f|)$, whereas $S_f$ denotes the
satisfying set~\cite{BRYANT86}. \tbr
